\em \huge A CONSTRVCTIVE SOLVTION TO THE K\"ONIGS-PITTSBVRGH BRIDGE PROBLEM

### 2016-03-07 koenigs/koenigs-pittsburgh.tex
some koenigs changes that were lying around from last year

  \title{\em \huge A CONSTRVCTIVE SOLVTION TO THE K\"ONIGS-PITTSBVRGH BRIDGE PROBLEM}
\author{Greg HANNEMAN\\
	Language Enthusiast and Errant Scribbler
	%\footnote{and Salaried Employee now too!}
	\\
        Carnegie Mellon Vniversity
	\and
	Benj. BLVM \\
	Light Cone Sedentarian \\
	Carnegie Mellon Vniversity}
\date{}
\pagestyle{empty}

@@

\begin{quote}
	,,At K\"onigsberg in Prussia there is an island A (Kneiphof), and flowing around it is divided into two branches, as shown in the figure; and the branches of the river, seven bridges, however, of this, \$a\$, \$B\$, \$C\$, \$d\$, \$e\$, \$F\$, and \$G\$. Already presented to him, the question concerning these bridges is, the course to be instructed so to whether a person may be able to, and not more than once in order to pass one by one the bridges honey themselves.''
\end{quote}

>>>>

  \title{\em \huge A CONSTRVCTIVE SOLVTION TO THE K\"ONIGS-PITTSBVRGH BRIDGE PROBLEM}
\author{Greg. HANNEMAN\\
	Language Enthusiast and Errant Scribbler
	%\footnote{and Salaried Employee now too!}
	\\
        Carnegie Mellon Vniversity
	\and
	Benj. BLVM \\
	Light Cone Sedentarian \\
	Carnegie Mellon Vniversity}
\date{}
\pagestyle{empty}

@@

\begin{quote}
	,,At K\"onigsberg in Prussia there is an island A known as Kneiphof, and flowing around it is divided into two branches, as shown in the figure; and the branches of the river, seven bridges, however, of this, \$a\$, \$B\$, \$C\$, \$d\$, \$e\$, \$F\$, and \$G\$. Already presented to him, the question concerning these bridges is, the course to be instructed so to whether a person may be able to, and not more than once in order to pass one by one the bridges honey themselves.''
\end{quote}
